flowCore: data structures package for flow cytometry data

### 2013-11-19 inst/doc/HowTo-flowCore.Rnw
merge from git
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@83412 bc3139a8-67e5-0310-9ffc-ced21a209358

There are also several immediate processing options
available in this function, the most important of which is
the \Rfunction{transformation} parameter, which can either
``linearize'' (the default) or ``scale'' our data. To
see how this works, first we will examine an FCS file
without any transformation at all:

@@

>>>>

There are also several immediate processing options
available in this function, the most important of which is
the \Rfunction{transformation} parameter, which can either
``linearize'' (the default) or ``linearize-with-PnG-scaling'' 
or ``scale'' our data. To see how this works, 
first we will examine an FCS file
without any transformation at all:

@@

The ``linearize-with-PnG-scaling'' option will perform the previous
transformation and it will also apply a ``division by gain''
to pamameters stored on linear scale with specified gain.
The gain is specified in the \$PnG keywords. This option has been introduced
as part of Gating-ML 2.0 compliance.
